On the combination of Set Functions and Failures

### 2015-04-02 docs/src/usage.tex
Added documentation for configurable profiling option
Manual extended w.r.t. hierarchical modules
Property definitions of the form "-Dprop=val" allowed as arguments

@@

\item[\fbox{\code{+/-profile}}]\pindex{profile}
Turn on/off the profile mode. If the profile mode is on,
expressions as well as programs are compiled with GHC's profiling
capabilities enabled. For expressions, evaluation will automatically
generate a file \code{Main.prof} containing the profiling information
of the evaluation.
For compiled programs, the profiling has to be manually activated
using runtime options when executed:
\begin{curry}
kics2 :set +profile :load MyProgram.curry :save :quit
./MyProgram +RTS -p -RTS [additional arguments]
\end{curry}

@@

\subsection{Command Line Editing}

>>>>

There are also some specific options that can be used
when invoking \CYS:
\begin{description}
\item[\code{--noreadline}:]
Do not use input line editing (see Section~\ref{sec-readline}).
\item[\code{-Dname=val}:]
Overwrite values defined in the configuration file \ccode{.kics2rc}
(see Section~\ref{sec-customization}),
where \code{name} is a property defined in the configuration file
and \code{val} its new value.
\end{description}

@@

\item[\fbox{\code{+/-profile}}]\pindex{profile}\index{profiling}
(only available when configured during installation, see Section~\ref{sec-install})
Turn on/off the profile mode. If the profile mode is on,
expressions as well as programs are compiled with GHC's profiling
capabilities enabled. For expressions, evaluation will automatically
generate a file \code{Main.prof} containing the profiling information
of the evaluation.
For compiled programs, the profiling has to be manually activated
using runtime options when executed:
\begin{curry}
kics2 :set +profile :load MyProgram.curry :save :quit
./MyProgram +RTS -p -RTS [additional arguments]
\end{curry}

@@

\subsection{Command Line Editing}
\label{sec-readline}
